### 2024-11-28 manuscript.tex
Fix issue in ANN description

On the RV \emph{Polarstern} voyages, regular human-performed synoptic
observations were available and included precipitation presence or absence and
type. We used this dataset to train a convolutional artificial neural network
(ANN) of the U-Net type \citep{ronneberger2015} to recognise profiles with
precipitation from lidar backscatter (Fig. \ref{fig:ann}a), implemented in the
TensorFlow ANN framework \citep{tensorflow}. Samples of short time intervals
(10 min) of near-surface lidar backscatter (0–250 m) were classified as clear,
rain, snow, and fog, using the synoptic observations as a training dataset
(Fig.  \ref{fig:ann}b). From these, a binary, mutually exclusive classification
of profiles as precipitating (rain or snow) or dry (clear or fog) was derived.
For detecting model and reanalysis precipitation, we used a fixed threshold for
surface precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).

>>>>

On the RV \emph{Polarstern} voyages, regular human-performed synoptic
observations were available and included precipitation presence or absence and
type. We used this dataset to train a convolutional artificial neural network
(ANN) to recognise profiles with precipitation from lidar backscatter (Fig.
\ref{fig:ann}a), implemented in the TensorFlow ANN framework
\citep{tensorflow}. Samples of short time intervals (10 min) of near-surface
lidar backscatter (0–250 m) were classified as clear, rain, snow, and fog,
using the synoptic observations as a training dataset (Fig.  \ref{fig:ann}b).
From these, a binary, mutually exclusive classification of profiles as
precipitating (rain or snow) or dry (clear or fog) was derived.  For detecting
model and reanalysis precipitation, we used a fixed threshold for surface
precipitation flux of 0.1 mm h$^{-1}$ (the ANN was not used).
